Finding Maximum $k$-Cliques Faster Using Lazy Global Domination

### 2016-05-17 paper/paper.tex
Review 3 comments

% cref style
\crefname{algocf}{algorithm}{algorithm}
\Crefname{algocf}{Algorithm}{Algorithms}
\crefname{figure}{figure}{figures}
\Crefname{figure}{Figure}{Figures}
\crefname{table}{table}{tables}
\Crefname{table}{Table}{Tables}

@@

A recent survey by \citeauthor{Shahinpour:2013} \shortcite{Shahinpour:2013} discusses algorithms and
results for $k$-clique and $k$-club problems .  We adopt their notation of $\tilde{\omega}_k$ for
the size of a maximum $k$-clique; the use of $\omega$ for the size of a maximum clique is standard.
They note that ``unlike the maximum clique problem, the maximum $s$-clique problem has not been the
subject of extensive research and we are not aware of any computational results for this problem to
date''. This is in contrast to the $k$-club problem, for which a wide range of computational results
are available
\cite{Bourjolly:2000,Bourjolly:2002,Mahdavi:2012,Hartung:2012,Chang:2013,Shahinpour:2013,Wotzlaw:2014,Picker:2015,Carvalho:2016}.

@@

We now give experimental results on a range of standard benchmarks, and on real-world and random
graphs. Experiments were run on a machine with dual Intel E5-2687W v3 processors and 256GBytes
RAM; single-threaded runtimes are given, except in \cref{table:parallel}, where 20 threads were used
(our machine does not have hyper-threading enabled). Our software was implemented in C++, using
C++11 native threads, and was compiled using GCC 5.1.0. The time taken to read in the graph from a
file is excluded, but preprocessing time (including the construction of $G^k$ and the bitset
encoding) is included. We use the term \emph{nodes} to refer to the number of recursive calls made
by the branch-and-bound part of the algorithm.

>>>>

% cref style
\crefname{algocf}{Algorithm}{Algorithm}
\Crefname{algocf}{Algorithm}{Algorithms}
\crefname{figure}{Figure}{Figures}
\Crefname{figure}{Figure}{Figures}
\crefname{table}{Table}{Tables}
\Crefname{table}{Table}{Tables}

@@

A recent survey by \citeauthor{Shahinpour:2013} \shortcite{Shahinpour:2013} discusses algorithms and
results for $k$-clique and $k$-club problems.  We adopt their notation of $\tilde{\omega}_k$ for
the size of a maximum $k$-clique; the use of $\omega$ for the size of a maximum clique is standard.
They note that ``unlike the maximum clique problem, the maximum $s$-clique problem has not been the
subject of extensive research and we are not aware of any computational results for this problem to
date''. This is in contrast to the $k$-club problem, for which a wide range of computational results
are available
\cite{Bourjolly:2000,Bourjolly:2002,Mahdavi:2012,Hartung:2012,Chang:2013,Shahinpour:2013,Wotzlaw:2014,Picker:2015,Carvalho:2016}.

@@

We now give experimental results on a range of standard benchmarks, and on real-world and random
graphs. Experiments were run on a machine with dual 3.1GHz Intel E5-2687W v3 processors and
256GBytes RAM; single-threaded runtimes are given, except in \cref{table:parallel}, where 20 threads
were used (our machine does not have hyper-threading enabled). Our software was implemented in C++,
using C++11 native threads, and was compiled using GCC 5.1.0. The time taken to read in the graph
from a file is excluded, but preprocessing time (including the construction of $G^k$ and the bitset
encoding) is included. We use the term \emph{nodes} to refer to the number of recursive calls made
by the branch-and-bound part of the algorithm.
